### 2008-12-19 talk/ecoop2009/jitgen.tex
make a figure

When the function is partially evaluated with respect to the TLC example
function shown in Figure XXX (which computes the absolute value of a number),
the residual code would look like in Figure \ref{fig:tlc-folded}. This version
is already a great improvement over pure interpretation, all the bytecode
dispatch overhead has been removed. However, the function as shown is still
rather inefficient, due to lots of superfluous stack handling and also due to
some indirect calls for implementing comparison (\lstinline{lt}) and
subtraction (\lstinline{sub}).

>>>>

When the function is partially evaluated with respect to the TLC example
function shown in Figure \ref{fig:tlc-abs} (which computes the absolute value of a number),
the residual code would look like in Figure \ref{fig:tlc-folded}. This version
is already a great improvement over pure interpretation, all the bytecode
dispatch overhead has been removed. However, the function as shown is still
rather inefficient, due to lots of superfluous stack handling and also due to
some indirect calls for implementing comparison (\lstinline{lt}) and
subtraction (\lstinline{sub}).
